\section{Conclusion}
\label{sec:conclusion}

This work addressed the problem of merging side outputs extracted from the convolutional layer model VGG to create region propositions for the task of image segmentation. We compare 3 different merging strategies to combine the side results: $add()$, $avg()$ and $max()$. The functions to enhance were evaluated using a cross-entropy and pixel-error loss functions. The impact of the number of side outputs was studied and compared to a version without any side outputs for a similar network architecture. At last, a simple mathematical morphology operation was proposed to  enhance the performance on the task and remove some noises. 

Experiments demonstrated that the $avg()$ function is viable for merging maps with different sizes and connotations, and could place the proposed strategy among the state-of-the-art approaches for the task on the Kitti dataset. The use of $avg()$ merging strategy was adopted before in \cite{liu2017}, but no explanation was given to the use of this method over other possible merging strategies. This paper helps to explain the good results achieved by those researchers.

It was also demonstrated that a large amount of side outputs increases the network capabilities during the training step and could also creates jumps that could lead to better performance, in terms of accuracy. The training graphs also shows that the number of side outputs contributes to a faster decay in loss function and stable results. The post-processing strategy slightly improved the performance, but requires further studies.

This research opens novel opportunities for study such as: (i) exploring different merging functions, less susceptible a values fluctuations;  (ii) exploring regularization techniques to sustain larger amounts of side outputs consistent; and (iii) insert the mathematical morphology kernels on the learning process to search for the best kernel size. 
 
The code  and a file containing all dependencies to reproduce the experiments is public available online in \url{https://github.com/falreis/segmentation-eval}. 

\section{Acknowledgements}
\label{sec:acknowledgements}

This paper acknowledges Github repositories \url{https://github.com/lc82111/Keras_HED} and \url{https://github.com/moabitcoin/holy-edge} that were helpful to provide some basic source codes used in this work.
